### 2024-03-27 doc/15yrsChange.Rmd
small edits to results text script & co-authors

---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

@@

<!--JOURNAL

Target journal:
Instructions for authors:
article type:  -->

@@

```{r eval = TRUE, echo = FALSE, warning = FALSE, results = 'hide'}
source("results-text-files.R")
```

@@

For the first time since the establishment of  the SCBI ForestGEO plot, whole-plot aboveground C stocks decreased over the 2018-2023 census interval (Figure 2) . From 2018 to 2023, whole-plot C stocks have decreased from `r wp_AGB_2018` to `r wp_AGB_2023` Mg C ha^-1^. Prior to this census interval, biomass

In regions with  high deer density and high canopy vulnerability AGB decreased significantly over the past two censuses, from `r hdhn_AGB_2013` Mg C ha^-1^ in 2013, to `r hdhn_AGB_2018` Mg C ha^-1^ in 2018, and `r hdhn_AGB_2023` Mg C ha^-1^ in 2023. Areas with low density of vulnerable canopy species experienced small losses of AGB between 2018 and 2023; inside and outside of the deer exclosure, biomass decreased from `r hdlv_AGB_2018` to `r hdlv_AGB_2023` Mg C ha^-1^  and `r ldlv_AGB_2018` to `r ldlv_AGB_2023` Mg C ha^-1^, respectively.

C stock decrease **is related to/ is explained by** above ground net biomass change. In the first two census intervals, 2008 to 2013 and 2013 to 2018, there were positive C fluxes, but for the 2018 to 2023 interval there was a negative C flux of **VALUE** Mg C/ha/year (Figure 3a).

>>>>

---

@@

Erika Gonzalez-Akre^1^

@@

@@

```{r eval = TRUE, echo = FALSE, warning = FALSE, results = 'hide', message = FALSE}
source("results-text-files.R")
```

@@

For the first time since the establishment of  the SCBI ForestGEO plot, whole-plot aboveground C stocks decreased over the 2018-2023 census interval (Figure 2) . From 2018 to 2023,ABG decreased from `r wp_AGB_2018` to `r wp_AGB_2023` Mg C ha^-1^. Prior to this, ABG had steadily increased at a rate of `r mean(awg_wholePlot_2013,awg_wholePlot_2018)` Mg C ha^-1^ yr ^-1^ between 2008 and 2018 (Figure 3a). In regions with  high deer density and high canopy vulnerability AGB decreased significantly over the past two censuses: from `r hdhn_AGB_2013` Mg C ha^-1^ in 2013, to `r hdhn_AGB_2018` Mg C ha^-1^ in 2018, and `r hdhn_AGB_2023` Mg C ha^-1^ in 2023. Areas with low density of vulnerable canopy species experienced small losses of AGB between 2018 and 2023; inside and outside of the deer exclosure, biomass decreased from `r hdlv_AGB_2018` to `r hdlv_AGB_2023` Mg C ha^-1^  and `r ldlv_AGB_2018` to `r ldlv_AGB_2023` Mg C ha^-1^, respectively.
